Flesh Simulation in the Field of Animation

### 2020-02-29 LaTeX-Master-Vorlage/chapter/Background.tex
improving paper chapter

\section{Deformation}
If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how do we formalize this in a mathematical construct?

@@

When deriving $\phi$, we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense:

\begin{align*}
&\text{Deformation gradient:} & \mathbf{F}&=\operatorname{\nabla} \phi \\
&\text{Length changes:} & \qquad I_{C}&=\operatorname{tr}\left(\mathbf{F}^{T} \mathbf{F}\right) \\
&\text{Volume changes:} & \qquad J&=\operatorname{det}(\mathbf{F})
\end{align*}

@@

\subsubsection{Polar Decomposition of the Deformation Gradient}
With the help of Thm. \ref{PD} we can decompose the deformation gradient into the following form:

@@

\subsection{Deformation Energy}
In order to get a convincing simulation of high quality one must choose an appropriate energy. In the case of modelling deformations on human-like characters an elastic energy needs to be chosen. The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back into its rest shape.
\\
The energy then has to be minimized in order to get the results we want.

>>>>

\subsection{Deformation}
If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how do we formalize this in a mathematical construct?

@@

When deriving $\phi$, we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense: 
\begin{align*}
&\text{Deformation gradient:} & \mathbf{F}&=\operatorname{\nabla} \phi \\
&\text{Length changes:} & \qquad I_{C}&=\operatorname{tr}\left(\mathbf{F}^{T} \mathbf{F}\right) \\
&\text{Volume changes:} & \qquad J&=\operatorname{det}(\mathbf{F})
\end{align*}

@@

\subsubsection{Polar Decomposition of the Deformation Gradient}
With the help of Thm.\ref{PD} we can decompose the deformation gradient into the following form:

@@

\subsection{Deformation Energy}
In order to get a convincing simulation of high quality, we have to choose an appropriate energy. In the case of modelling deformations on human-like characters an elastic energy needs to be chosen. The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero, the object must come back into its rest shape.
\\
The energy then has to be minimized in order to get the results we want.

### 2020-02-29 LaTeX-Master-Vorlage/chapter/paper.tex
improving paper chapter

\chapter{Paper} \label{c:Paper}
In this chapter I will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}. In the interest of understanding the thought process of the authors I will include some of their calculations a bit more detailed. In addition examples and visualisations should help for a better perception.

\section{Deformation Gradient}
In the following calculations some properties of the deformation gradient $\mathbf{F}$ covered in the background chapter will be used. These properties are summarized in table \ref{table:gradient_quantities} for a better overview:

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Symbol} & \textbf{Definition} \\ \hline
    $\mathbf{F} = \mathbf{RS}$ & Polar decomposition \\ \hline
    $J=\operatorname{det}(\mathbf{F})$ & Relative volume change \\ \hline
    $\mathbf{C}=\mathbf{F}^\intercal \mathbf{F}$ & Right Cauchy-Green  \\ \hline	
    $I_{C}=\operatorname{tr}(\mathbf{C})$ & First right Cauchy-Green invariant \\ \hline
    \end{tabular}
    \caption{Quantities Derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
\label{table:gradient_quantities}
\end{table}

@@

\subsection{Stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. They concentrated on the deformation energy. In order to achieve a convincing result the first step is to specify some requirements. For our needs in this case the stability of the energy is important. More precisely we need a hyperelastic energy that is stable in the following four important ways:

\textbf{1. Inversion Stability:} Given some arbitrary object it is possible that while deforming the object one can arrive at a zero volume state or even an entire inversion. Take for example the tetrahedron shown in figure \ref{fig:inversion_1}. In figure \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle. In figure \ref{fig:inversion_3} image we have an inversion of the object. The needed deformation energy has to be able to deal with both cases. That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).

>>>>

\chapter{Stable Neo-Hookean Flesh Simulation} \label{c:Paper}
In this chapter, I will examine further the topic of the paper \textit{\acrshort{snh}}. In the interest of understanding the thought process of the authors, I will include some of their calculations more detailed. In addition, examples and visualisations are presented for a better understanding.

\section{Deformation Gradient}
In the following calculations some properties of the deformation gradient $\mathbf{F}$ covered in chapter 2 will be used. These properties are summarized in table \ref{table:gradient_quantities} for a better overview:

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Symbol} & \textbf{Definition} \\ \hline
    $\mathbf{F} = \mathbf{RS}$ & Polar decomposition \\ \hline
    $J=\operatorname{det}(\mathbf{F})$ & Relative volume change \\ \hline
    $\mathbf{C}=\mathbf{F}^\intercal \mathbf{F}$ & Right Cauchy-Green  \\ \hline	
    $I_{C}=\operatorname{tr}(\mathbf{C})$ & First right Cauchy-Green invariant \\ \hline
    \end{tabular}
    \caption{Quantities derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
\label{table:gradient_quantities}
\end{table}

@@

\subsection{Stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. The focus of the authors was the deformation energy. In order to achieve a convincing result the first step is to specify some requirements. Firstly the energy has to be stable. More precisely, we need a hyperelastic energy that is stable in the following four important ways:

\textbf{1. Inversion Stability:} Given some arbitrary object, it is possible that while deforming the object one can arrive at a zero volume state or even an entire inversion. Take for example the tetrahedron shown in Fig. \ref{fig:inversion_1}. In Fig. \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle. In Fig. \ref{fig:inversion_3} we have an inversion of the object. The deformation energy has to be able to deal with both cases. That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).
